\documentclass[../../DD.tex]{subfiles}
\begin{document}
\section{Purpose and scope}
\textit{Ventour} is an Italian Venture Capital Company that operates in 4 main areas:
\begin{itemize}
    \item Technology
    \item Healthcare
    \item Consumer Goods
    \item Sustainability
\end{itemize}
The goal of the company is to enhance the capability of the start-ups in order to make them big.
The motto of the company is:
\begin{center}
    \textit{Transforming the investment landscape and fueling inovation.}
\end{center}
    Ventour gives to the new companies the possibilities to be helped, playing a crucial role in the process of funding and supporting early-stage and high-growth companies.

    The most important section of the website in order to attract new company to invest in, is the one where the most relevant project are shown. They are shown both in the home page or also in the Investment page, clicking on the filter "most relevant".

    Another important section that can be read carefully by a possible new company, is the History. Indeed, in about us, there are some useful information about the company in the past and in the present.  

    The website also provides a clear process for entrepreneurs to submit their proposals or connect with the investment team, that can be achieved going in "Get in touch" page.

    Last but not least Ventour shows the people who work in the company and manage the relationship between the team and the companies. Maybe the new clients will ask about specific team leaders or in general people that they saw on the website.  \\
    Indeed, new clients can read the description of people who work there and trust in them, and so in the company.

    \paragraph{Details of the website} The website also show user some key numbers about the productivity of the Ventour Capital company and of the members of the teams, highlighting their expertise and experience. This helps establish credibility and builds trust with potential investors and entrepreneurs.

    It is important to keep in contact with the company. It is the reason why users can send an email by clicking on "join us" in the homepage, or also clicking on the e-mail in the footer.

    Branding and reputation management: The website plays a crucial role in establishing and reinforcing the brand identity and reputation of Ventour Capital. It should reflect the company's values, professionalism, and commitment to excellence in venture capital investments.

    In the Home Page it is possible to see also the internationality of the company, looking at all the numbers that well describe the results of the company.
\end{document}
